What do incoming university students believe about open science practices in

### 2022-03-21 analysis/Manuscript.Rmd
analyse awareness by major

library(papaja) #install with devtools
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(tidyselect) 
library(broom)
library(irr)

@@

psyc_major <- df %>% 
  filter(major_recoded)

@@

>>>>

if(! requireNamespace('box')) {
  install.packages('box')
}

library(papaja) #install with devtools
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(tidyselect) 
library(broom)

box::use(irr[agree,kappa2]) # load just these two functions from the `irr` package

@@

psyc_major <- df %>% 
  select(c(major_recoded, crisis)) %>% 
  na.omit() # remove NAs

not_psyc <- psyc_major %>% 
  filter(major_recoded == "Not psychology")

psyc <- psyc_major %>% 
  filter(major_recoded == "Psychology")

# run the chi-square
psyc_major_table <- table(psyc_major)

chi <- chisq.test(psyc_major_table)

@@

At a reviewer's request, we ran an additional exploratory analysis to determine whether
the proportion of students who are unaware of the replication crisis differs between psychology 
and non-psychology majors. We were able to code the majors for `r length(psyc_major$major_recoded)` students; of these `r round(length(psyc$crisis)/length(psyc_major$crisis)*100, 0)`% reported that psychology was their major.

Of those majoring in psychology, `r round(sum(psyc$crisis==1)/length(psyc$crisis)*100,0)`% indicated that they 
were aware of the replication crisis. Of those majoring in another program other than psychology, 
`r round(sum(not_psyc$crisis==1)/length(not_psyc$crisis)*100,0)`% indicated that they were aware of the replication crisis. A chi-square test of independence indicated that there was no significant difference between psychology
majors and non-majors in terms of their self-reported awareness of the replication crisis, X^2^ (`r chi$parameter`) = `r round(chi$statistic,2)`, *p* = `r round(chi$p.value,2)`. 
This lack of a signficant difference should be replicated in a larger population; however, it suggests that psychology instructors should not presume that students choosing to major in psychology are aware of the replication crisis.
